Letter to Editor

### 2024-03-25 rawfiles/letter_to_ed.qmd
final (hopefully) version

---
title: Letter to Editor
author: David Hood
date: last-modified
format: gfm
bibliography: references.bib
---

*The timetable is: On Friday 22nd I will be distribution the final draft to people who have expressed an interest in co-signing, with an aim to send it to the journal early in the week beginning Monday 25th.*

>>>>

---
date: last-modified
format: gfm
bibliography: references.bib
---
